---
title: "Steph Sierra Mosquitos"
author: "Zoe"
date: "6/1/2022"
output:
  html_document: default
  pdf_document: default
---

# Preliminary Data Fun Times

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
#library(MASS)
#install.packages("lme4")
library(lme4)
```

*John’s Data*
```{r reading in data and cleaning}
mosq <- read_csv("mosq2019_sjc.csv") %>% 
  #for analyses, only need fish (ind), elevation (ind), lake?, direction (ind) trap_id (random), date (random), tot_mosq(response var)
  dplyr::select(tot_mosq, fish, elevation, lake, trap_id, date, direction)

# fish needs to be a factor:
mosq$fish <- factor(mosq$fish)
mosq$elevation <- factor(mosq$elevation, levels = c("low", "mid", "high"))
```

## let's do some visualization to see where our patterns/variation is. I like to use scatter plots
steph's qs:  
- What happens to abundance by trap night?  
- Does it systematically decrease?   
- Some effect of cardinal direction?  
  
```{r data vis}
trap_id_effect <- ggplot(mosq, aes(x = elevation, y = tot_mosq)) +
  geom_point(aes(color = trap_id))
trap_id_effect
# new mac is broken so to ggplot, have to copy graph name and put in console

# no noticable effect of trap_id, should prob code as random

date_effect <- ggplot(mosq, aes(x = date, y = tot_mosq)) +
  geom_point()
date_effect
#maybe an increase in mosquitoes by date? might want to include an interaction of date and elev in model

fish_effect <- ggplot(mosq, aes(x = fish, y = tot_mosq)) +
  geom_point(aes(color = elevation))
# more mosquitoes with fish
fish_effect

direction_effect <- ggplot(mosq, aes(x = direction, y = tot_mosq)) +
  geom_point(aes(color = elevation))
# N and S facing traps look like they have more mosquitoes
direction_effect

```

*Box/Whisker plots of the data*  
Tejon style box plots would be nice  
  
What is the variation treatment (fish) by level (elevation)?  

```{r boxplots}
# boxplot with differences between fish/no fish, facet wrapped by elevation (hi/med/lo)
fish_elev <- ggplot(mosq, aes(x = fish, y = tot_mosq)) +
  geom_boxplot()+
  facet_wrap(vars(elevation))
fish_elev
# no big diff at high, big diffs at low and med

```

What's the distribution of the data?
```{r distribution}

hist <- ggplot(mosq, aes(x = tot_mosq)) +
  geom_histogram(aes(fill = elevation))
hist

# lol aggregated af
# high elev data might be more normal, but not by much
# definitely run w/ a negative binomial distribution instead of a poisson
```

## Models? 
**Mixed effect model - Mos abundance = Fish status (Y/N) + Elevation (High, Medium, Low) + Fish:Elevation + site (random)**

What’s the replicate?  

Every night and/or every trap as if it was an independent sample? (every night is how data is set currently)  

Pooling them to a single trap?  

Or run with random effect of Trap ID?  

What is the result of that? Is there something we can confidently say is significant?  

```{r}

### response variable is count data, so 

### W'RE DUMN and tried to run this with 

#m1 <- glm(tot_mosq ~ fish + elevation + fish*elevation + 1|trap_id, family = "binomial", link = "logit")

### https://stats.oarc.ucla.edu/r/dae/negative-binomial-regression/ <- doesnt work with mixed effects

#m1 <- glm.nb(tot_mosq ~ fish + elevation + (fish*elevation) + 1|trap_id, data = mosq, link = log)

### https://rdrr.io/cran/lme4/man/glmer.nb.html <- glmer.nb from the lme4 package does!
m1 <- glmer.nb(tot_mosq ~ fish + elevation + (fish*elevation) + (1|direction), data = mosq)
m1

```


# Importing GPX data and measuring lake area

```{r setup}
require(maptools) # apparently being retired end of 2023
require(rgdal) # same
require(sf)


## from other importing gpx markdown ##
library(plotKML)
library(tidyverse)
library(ggmap)
register_google(key = "AIzaSyBArxYrAlB60bafi6iGDYGtWox6ZIgylNg")
# had to register a key with personal email because the zilz@ucsb.edu one is all on the fritz about billing nonsense SO

# maybe need?
library(maps)
library(sf)
library(rnaturalearth)
```

```{r reading and cleaning data}

#readOGR is in maptools

coney <- readOGR(dsn= "Track_2022-06-29 1027 CONEY EDGE.gpx", layer = "tracks")

str(coney)


```

```{r plotting and getting area}

plot(coney) #doesnt look like much and we can't calc area, but it's a start

# using package sf to convert, hopefully
coney_sf <- st_as_sf(coney) # converts to shapefile
coney_poly <- st_polygonize(coney_sf) # converts to polygon? still a sf dataframe
##coney <- as(coney_poly, "Spatial") # If you want sp NOT WRKING


```


