---
title: "Steph Sierra Mosquitos"
author: "Zoe"
date: "6/1/2022"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
```

*John’s Data*
```{r reading in data and cleaning}
mosq <- read_csv("mosq2019_sjc.csv") %>% 
  #for analyses, only need fish (ind), elevation (ind), lake?, direction (ind) trap_id (random), date (random), tot_mosq(response var)
  select(tot_mosq, fish, elevation, lake, trap_id, date, direction)

# fish needs to be a factor:
mosq$fish <- factor(mosq$fish)
mosq$elevation <- factor(mosq$elevation, levels = c("low", "mid", "high"))
```

## let's do some visualization to see where our patterns/variation is. I like to use scatter plots
steph's qs:  
- What happens to abundance by trap night?  
- Does it systematically decrease?   
- Some effect of cardinal direction?  
  
```{r data vis}
trap_id_effect <- ggplot(mosq, aes(x = elevation, y = tot_mosq)) +
  geom_point(aes(color = trap_id))
trap_id_effect
# new mac is broken so to ggplot, have to copy graph name and put in console

# no noticable effect of trap_id, should prob code as random

date_effect <- ggplot(mosq, aes(x = date, y = tot_mosq)) +
  geom_point()
date_effect
#maybe an increase in mosquitoes by date? might want to include an interaction of date and elev in model

fish_effect <- ggplot(mosq, aes(x = fish, y = tot_mosq)) +
  geom_point(aes(color = elevation))
# more mosquitoes with fish

direction_effect <- ggplot(mosq, aes(x = direction, y = tot_mosq)) +
  geom_point(aes(color = elevation))
# N and S facing traps look like they have more mosquitoes

```

*Box/Whisker plots of the data*  
Tejon style box plots would be nice  
  
What is the variation treatment (fish) by level (elevation)?  

```{r boxplots}
# boxplot with differences between fish/no fish, facet wrapped by elevation (hi/med/lo)
fish_elev <- ggplot(mosq, aes(x = fish, y = tot_mosq)) +
  geom_boxplot()+
  facet_wrap(vars(elevation))
fish_elev
# no big diff at high, big diffs at low and med

```


Mixed effect model - Mos abundance = Fish status (Y/N) + Elevation (High, Medium, Low) + Fish:Elevation

What’s the replicate?  

Every night and/or every trap as if it was an independent sample? (every night is how data is set currently)  

Pooling them to a single trap?  

Or run with random effect of Trap ID?  

What is the result of that? Is there something we can confidently say is significant?  





